\begin{thebibliography}{99}

%Intro%\cite{PAC37Proposal}

\bibitem{HPS_PROP} A. Grillo {\it et al.} [HPS Collaboration], HPS Proposal to JLab PAC37 PR-11-006,
 http://www.jlab.org/exp\_prog/PACpage/PAC37/proposals/Proposals/

\bibitem{HPS_tPROP} A. Grillo {\it et al.} [HPS Collaboration], HPS Test Run Proposal to DOE, 
https://confluence.slac.stanford.edu/display/hpsg/Project+Overview

\bibitem{HPS_PROP_UPD} P. Hansson {\it et al.} [HPS Collaboration], HPS Update PAC 39, 
https://confluence.slac.stanford.edu/display/hpsg/Project+Overview

%motivation
\input{bib_motivation}
\input{bib_muonium}
%%
 
\bibitem{elegant} M. Borland, A Flexible SDDS-Compliant Code for Accelerator Simulation, ANL, Argonne, IL 60439, USA
 
\bibitem{slic}  http://www.lcsim.org/software/slic/
 
\bibitem{trackAlgo} P. Billoir, R. Fruhwirth, and M. Regler, Nucl. Instr. And Meth. A241 (1985) 115. 

\bibitem{vertexAlgo}  . P. Billoir and S. Qian, Nucl. Instr. And Meth. A311 (1991) 139. 

\bibitem{Jones:1069892} L. Jones, APV25-S1: User guide version 2.2, RAL Microelectronics Design Group, 2011.

\bibitem{Raymond:2002yr} M. Raymond et al., APV25 production testing and quality assurance, 8th Workshop on Electronics for LHC
	              Experiments, Colmar, France, 9-13 Sep 2002
	               
\bibitem{atca} PICMG 3.0 Revision 2.0 AdvancedTCA Base Specification, http://www.picmg.org

\bibitem{egs5} The EGS5 Code System, H. Hirayama, Y. Namito, A.F. Bielajew, S.J. Wilderman and W.R. Nelson, SLAC-R-730 and KEK Report 2005-8 (2005).

\bibitem{geant4}  Allison, J. et al, "Geant4 developments and applications," Nuclear Science, IEEE Transactions on , vol.53, no.1, pp.270-278, Feb. 2006; S. Agostinelli et al , "Geant4Ña simulation toolkit," NIM A506, 250-303 (2003)







\end{thebibliography} 